---
title: 'Applied Predictive Modelling : Chapter 3'
output: pdf_document
---
Loading the required packages
```{r}
library(e1071)
library(ggplot2)
library(caret)
library(plyr)
```
Loading the required data 
```{r}
load("/home/nitin/Downloads/AppliedPredictiveModeling/data/segmentationOriginal.RData")
d = segmentationOriginal
```

Subsetting the Data
```{r}
segData <- subset(segmentationOriginal, Case == "Train")

cellid <- segData$Cell
class <- segData$Class
case <- segData$Case

segData <- segData[,-(1:3)]

statusColNum <- grep("Status", names(segData))
segData <- segData[,-statusColNum]
```

***Calculate skewness of data***
```{r}
skewness(segData$AngleCh1)
# Compute skewness across all columns
skewValues <- apply(segData, 2, skewness)
```

***Example, to Box–Cox transform, center, and scale the data, then execute PCA for signal extraction :***
```{r}
trans <- preProcess(segData, method = c("BoxCox", "center", "scale", "pca"))

## Apply the above transformation to segData
transformed <- predict(trans, segData)
head(transformed[,1:5])
```

***Filter nearZero variance predictors***
```{r}
nearZeroVar(segData)
```

***Calculating correlation between predictors***
```{r}
correlations <- cor(segData)
dim(correlations)
correlations[1:4,1:4]
```

***Correlation plot***
```{r}
library(corrplot)
corrplot(correlations, order = "hclust")
```

***Filtering based on correlations. (Predictors recommended for deletion)***
```{r}
highCorr <- findCorrelation(correlations, cutoff = 0.75)
length(highCorr)
filteredSegData <- segData[,-highCorr]
names(filteredSegData)
```















